Decorrelating Errors in Quantum Gates by Random Gate Synthesis

### 2018-03-14 decorrelation.tex
adding bib, and first pass at some way of writing algorithms

\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
%\hypersetup{citecolor={blue}, colorlinks={true}, filecolor={blue},
%   linkcolor={blue}, pdfauthor=, pdfkeywords= pdfsubject=, pdftitle=,
%   urlcolor{blue}}

@@

After using GRAPE to produce a collection of controls, we now must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}). To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate. If we consider the Pauli-Liouville representation of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations. In particular, we see that we can write a convex sum over these channels as:
\begin{align}
 \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}
\end{align}
Now, to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
\begin{equation}
  \begin{align}
   &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
   &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
   &\textbf{subject to} \sum_{i=1}^Nw_i = 1
  \end{align}
\end{equation}

@@

@@

$$ \epsilon, \delta \midtilde \sim \mathcal{N}(0, .001) $$
$$\epsilon_0, \epsilon_1, \delta_0, \delta_1 \midtilde \sim \mathcal{N}(0, .001)$$
% \bibliography{decorrelation.bib}

\end{document}

>>>>

\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm, algorithmicx}
\usepackage{algpseudocode}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
%\hypersetup{citecolor={blue}, colorlinks={true}, filecolor={blue},
%   linkcolor={blue}, pdfauthor=, pdfkeywords= pdfsubject=, pdftitle=,
%   urlcolor{blue}}

@@

After using GRAPE to produce a collection of controls, we now must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}). To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate. If we consider the Pauli-Liouville representation of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations. In particular, we see that we can write a convex sum over these channels as:
\begin{align}
 \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}
\end{align}
Now, to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
\begin{align}
   &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
   &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
   &\textbf{subject to} \sum_{i=1}^Nw_i = 1
\end{align}

@@

\section{GRAPE}
First described in \cite{Khaneja2005}, the GRAPE (GRadient Ascent Pulse Engineering) algorithm is a technique for finding piecewise constant control sequences that approximate a desired unitary. Naively this can be done by defining a cost function $J(U) = Tr\{U_TU\}$, where $U_T$ is the target unitary, and $U = \exp\{-it(H_0 + \sum_{i=0}^{n}(c_i(t)H_i)\}$. One can then define the \textit{control matrix} $u_{ij}$, denoting the control amplitude associated with the $i^{th}$ time step and the $j^{th}$ hamiltonian. Then we see that we can maximize our cost function via the chain rule, i.e. performing the following update loop for some threshold value $\delta$:

\begin{algorithmic}
\Procedure{find\_controls}{U, $\delta$, $u_{ij}$}
\While{$J(U) < (1-\delta$)}
\State $u_{ij}$ $\rightarrow$ $u_{ij} + \epsilon\frac{\partial J(U)}{\partial u_{ij}}$
\State $U \rightarrow \exp\{-it(H_0 + \sum_{i=0}^{n}(c_i(t)H_i)\}$
\EndWhile
\EndProcedure
\end{algorithmic}

In general these gradients can be computed via simple back propagation with the chain rule, however in \cite{Khaneja2005} Khaneja et al. derives a simple update formula that is correct to first order. So long as the discretization in time is fine enough,this will be a good approximation.

@@

%$$ \epsilon, \delta \midtilde \sim \mathcal{N}(0, .001) $$
%$$\epsilon_0, \epsilon_1, \delta_0, \delta_1 \midtilde \sim \mathcal{N}(0, .001)$$
\bibliography{decorrelation.bib}
\end{document}
